Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation

### 2011-02-14 Multiresolution_framework/ltx/manuscript.tex
added observation equation

where the local post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$, parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$ where $\tau$ is the synaptic time constant and $T_s$ is the sampling time. The spatial connectivity between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$, for an isotropic and homogeneous neural field. The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}. The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the sigmoidal activation function $f\left(.\right)$. The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}. Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function

@@

For simplicity, 

@@

The spatially homogeneous, linear IDE is given by
 z_{t+1}\left(\mathbf{s}\right)=\int_{\mathcal{S}}k\left(\mathbf{s}-\mathbf{r}\right)z_{t}\left(\mathbf{r}\right)d\mathbf{r}+e_{t}\left(\mathbf{s}\right)
\label{eq:ConvolutionIntegral}
where $t\in \mathbb{Z}_0 $ denotes discrete time, $\mathbf{s},\mathbf{r} \in \mathcal{S} \subset \mathbb{R}^{n_\mathcal{S}}$ are spatial locations in $n_{\mathcal S}$-dimensional physical space, where $n_{\mathcal S} \in \left\lbrace 1,2,3 \right\rbrace $. The continuous spatial field at time $t$ and at location $\mathbf s$ is denoted $z_t\left(\mathbf s\right)$. The model dynamics  are defined by the homogeneous time invariant spatial mixing kernel, $k\left(\mathbf{s}-\mathbf{r}\right):\mathbb{R}^{n_\mathcal{S}}\rightarrow \mathbb{R}$ which maps the current spatial field to the next spatial field via the integral (\ref{eq:ConvolutionIntegral}) and $e_t(\mathbf s)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$.  Here $\mathcal{GP}(\mathbf 0,\eta(\mathbf{s}-\mathbf{r}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}. The spatial field is observed by
 \mathbf{y}_{t}=\mathbf{z}_{t}+\mathbf{v}_t
\label{eq:observation equation}
where the observation vector $\mathbf{y}_{t}=[y_t(\mathbf{s}_1) y_t(\mathbf{s}_2)\cdots y_t(\mathbf{s}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations and at time $t$, is corrupted by an i.i.d normally distributed zero-mean white noise $\mathbf{v}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{v}\right)$ with $\mathbf{\Sigma}_{v}=\sigma_v^2\mathbf I_{n_y} $. It is assumed here that $\boldsymbol\Sigma_v$ and $\eta\left(\mathbf s-\mathbf r \right)$ are known. The superscript $\top$ denotes the transpose operator.

>>>>

where the local post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$, parameter $\xi=\left(1-\frac{ T_s}{\tau}\right)$ where $\tau$ is the synaptic time constant and $T_s$ is the sampling time. The spatial connectivity between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$, for an isotropic and homogeneous neural field. The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977}. The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the sigmoidal activation function $f\left(.\right)$. The term $e_t(\mathbf r)$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{s})\sim\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$, where $\mathcal{GP}(\mathbf 0,\eta(\mathbf{r}-\mathbf{r'}))$  denotes a zero mean spatial Gaussian process with covariance function $\eta(\mathbf{r}-\mathbf{r'})$~\cite{Rasmussen2005}. For simplicity, we denote hereafter the current time step by $t$ and the future time step by $t+1$. Here we assume that the sigmoid activation function, $f(\cdot)$, can be approximated by the piecewise function

@@

observation equation is given by 
\begin{equation}\label{eq:ObservationEquation}
	\mathbf y_t = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 
where electrophysiological recordings $\mathbf{y}_{t}=[y_t(\mathbf{r}_1) y_t(\mathbf{r}_2)\cdots y_t(\mathbf{r}_{n_y})]^\top$, compiled at $n_{y}$ spatial locations and at time $t$ via the observation kernel  $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$, is corrupted by an i.i.d normally distributed zero-mean white noise $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ with $\mathbf{\Sigma}_{\epsilon}=\sigma_{\epsilon}^2\mathbf I_{n_y} $. The superscript $\top$ denotes the transpose operator.

@@
